Data Analysis Methods for the Detection of the Epoch of Reionization

### 2017-11-22 PAPER.tex
-Most of Jonnie's edits all accounted for except: appendix, and a few outstanding issues

\cc{Should we even include this next section? I included it to follow-up on Section 2.3.1, but it's not saying anything new...}

@@

Although current $21$ cm published power spectrum upper limits lie a couple orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife and null tests.

@@

\begin{itemize}
\item Signal loss, previously found to be $<2\%$ in P64, was underestimated by a factor of $\sim$$1000$ for inverse covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a factor of $\sim7$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also revised from new signal loss calculations associated with their singular value decomposition foreground filter.
\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering. They were also overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power spectra (Section \ref{sec:Boot}). Hence, the net change for our error estimation is negligible, though the rationale behind the previous estimation was incorrect.
\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a decrease in predicted sensitivity level by a factor of $\sim$$3$ in mK (Section \ref{sec:PSSense}). We have verified our revised prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that the theoretical prediction for noise in P64 was too high for its data points.
\end{itemize}

@@

\section{Acknowledgements}
CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions. PAPER and HERA are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, JCP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1302774, 1401708, and 1455151, respectively). We also graciously thank SKA-SA for site infrastructure and observing support.
\label{sec:Ack}

>>>>

@@

Although current $21$ cm published power spectrum upper limits lie several orders of magnitude above predicted EoR levels, ongoing analyses of deeper sensitivity datasets from PAPER, MWA, and LOFAR, as well as next generation instruments like HERA, are expected to continue to push towards EoR sensitivities. As the field progresses towards a detection, we have shown that it is crucial for future analyses to have a rigorous understanding of signal loss in an analysis pipeline, be able to accurately and robustly calculate both power spectrum and theoretical errors, and consistently undergo a comprehensive set of jackknife and null tests.

@@

\begin{itemize}
\item Signal loss, previously found to be $<2\%$ in P64, was underestimated by a factor of $\sim$$1000$ for inverse covariance weighting. For our new analysis, we use a regularized covariance weighting method to minimize loss (Section \ref{sec:Weight}). However, because our revised weighting method is not as aggressive as the former, our results are still a factor of $\sim7$ mK higher than previous limits. Underestimated signal loss therefore represents the bulk of our revision. We note that PAPER's analysis is not the first to underestimate loss; results from the GMRT (\citealt{paciga_et_al2013}) were also revised from new signal loss calculations associated with their singular value decomposition foreground filter.
\item Power spectrum errors, originally computed by bootstrapping, were underestimated by a factor of $\sim$$2$ due to oversampling data whose effective number of independent samples was reduced from fringe-rate filtering. They were also overestimated by a factor of $\sim$$2$ from using a suboptimal way of combining baselines into groups when forming power spectra (Section \ref{sec:Boot}). Hence, the net change for our error estimation is negligible, though the rationale behind the previous estimation was incorrect.
\item Several factors used in an analytic expression to predict the noise-level in PAPER-64 data were revised, yielding a decrease in predicted sensitivity level by a factor of $\sim$$3$ in mK (Section \ref{sec:PSSense}). We have verified our revised prediction extensively using pure noise simulations. We note that our sensitivity prediction is revised by a factor less than our power spectrum result, implying that if taken at face value, the theoretical prediction for noise in P64 was too high for its data points.
\end{itemize}

@@

\section{Acknowledgements}
CC would like to acknowledge the UC Berkeley Chancellor's Fellowship, National Science Foundation Graduate Research Fellowship (Division of Graduate Education award 1106400), and thank Eric Switzer for helpful discussions. PAPER and HERA are supported by grants from the National Science Foundation (awards 1440343, and 1636646). ARP, DCJ, and JEA would also like to acknowledge NSF support (awards 1352519, 1401708, and 1455151, respectively). We also graciously thank SKA-SA for site infrastructure and observing support.
\label{sec:Ack}
